---
title: "Shiny Application and Reproducible Pitch"
output: ioslides_presentation
date: "30 October 2017 // Emilia CL"

---
<style type="text/css">

body{ /* Normal  */
      font-size: 8px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 28px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 15px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assigment

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on     either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and    it must contain a plot created with Plotly. 

Your Shiny Application: the application allows you to apply clusters to groups of mtcars data

Reproducible Pitch: RMarkdown-Presentation(ioslides)

Data used: Mtcars / cluster method


## mtcars data


The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on 11 variables.

variables:

[, 1]	 mpg	 Miles/(US) gallon;
[, 2]	 cyl	 Number of cylinders;
[, 3]	 disp	 Displacement (cu.in.);
[, 4]	 hp	 Gross horsepower;
[, 5]	 drat	 Rear axle ratio;
[, 6]	 wt	 Weight (1000 lbs);
[, 7]	 qsec	 1/4 mile time;
[, 8]	 vs	 V/S;
[, 9]	 am	 Transmission (0 = automatic, 1 = manual);
[,10]	 gear	 Number of forward gears;
[,11]	 carb	 Number of carburetors;



## mtcars data

```{r, fig.align='center', message = FALSE}
data(mtcars)
dim(mtcars)
str(mtcars)
```

## Aplication


The application was inspired by an example cluster application.
Modifications were made to the dataset, data visualization, layout components, input configuration and added new inputs to shinny code.

How to use: you can choose your group variables to cluster, and the cluster number. A interactive plot and text are displayed

"k-means clustering is a method of vector quantization, that is popular for cluster analysis in data mining. k-means clustering aims to partition n observations into k clusters in which each observation belongs to the cluster with the nearest mean..." 

App shinny : https://emiliamcl.shinyapps.io/shiny_2_final_assigment/

## App.server

      function(input, output, session) {
      selectedData <- reactive({
       mtcars[, c(input$xcol, input$ycol)]
     })
        clusters <- reactive({
       kmeans(selectedData(), input$clusters)
     })
      output$plot1 <- renderPlot({
       palette(c("#B287A3", "#ECCE8E", "#5F787A", "#984EA3",
              "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999","#BDCFB5"))

      plot(selectedData(),
           col = clusters()$cluster,
           pch = 20, cex = 3)
      points(clusters()$centers, pch = 1, cex = 3, lwd = 2.5)
      })
        output$txtout <- renderText({
        paste(input$clusters, "clusters", "-", "xvariable" ,input$xcol,"and", "yvariable",input$ycol)})
      }

### Other files
Github

https://github.com/emiliamcl/datasciencecoursera/tree/master/Developing-Data-Products


### Thanks



